### 2016-05-23 intro.tex
cheers

\tsnote{UPDATE (5/20/16): I'm now convinced that what they call memory size~$m$, when applied to real Bloom filters, is \emph{only} the size of the bit array, and does \emph{not} include a description of the hash functions.  The memory size comparisons that are made throughout the paper are to classical memory lowerbounds that account only for the bitsize of the array. Concretely: in the abstract they say ``... we show there exists a Bloom filter for sets of size~$n$ and error~$\epsilon$, that is secure against~$t$ queries and uses only $O(n\log\frac{1}{\varepsilon} + t)$ bits of memory.  In comparison, $n \log\frac{1}{\varepsilon}$ is the best possible under a non-adaptive adversary.''  The latter bound is the classical one.   If you look in the paper for this actual result, it's in Theorem 6.2.   So, we look at the theorem and the construction that proves it.  It uses a specially constructed function~$g$ and a Cuckoo hashing dictionary~$D$, consisting of two tables~$T_1,T_2$ and two hash functions~$h_1,h_2$.  Here is a quote from the proof ``The final memory of the Bloom filter is the memory of~$D$ and the representation of~$g$.  The dictionary~$D$ consists of $O(n)$ cells, each of size $|g(x)|=O(\log\frac{1}{\varepsilon})$ bits and therefore~$D$ and~$g$ together can be represented using $O(n\log\frac{1}{\varepsilon} + t)$ bits'', where earlier they say ``the representation of~$g$ requires $O(t)$ bits''.  Thus they are \emph{not} considering the size of the hash functions~$h_1,h_2$ that are used to populate the cells of~$D$.   So, as I said, I'm now convinced that their Bloom filter syntax does not actually capture real Bloom filters.}

Finally, the security definitions do not give the adversary access to the hash functions that created the representation; effectively, they are secret.  This strikes me as quite odd, and seems to miss the point that finding a false positive should be hard, in practice, even if you know that the hash functions are, say,  $h_i(X)=\mathrm{SHA256}(\langle i \rangle \concat X)$.  (If the hash functions are not kept secret, the whole [NY] security notion kind of unravels; the adversary already is given~$S$, so if it knows the hash functions then you might as well just give it the whole Bloom filter data structure.) \tsnote{In the Squid proxy, the hash functions are not secret: you can download the source code, and the docs~\footnote{http://wiki.squid-cache.org/SquidFaq/CacheDigests} (available online even!) tell you that ``The protocol design allows for a variable number of hash functions (k). However, Squid employs a very efficient method using a fixed number - four. {\bf Rather than computing a number of independent hash functions over a URL Squid uses a 128-bit MD5 hash of the key (actually a combination of the URL and the HTTP retrieval method) and then splits this into four equal chunks. Each chunk, modulo the digest size (m), is used as the value for one of the hash functions - i.e. an index into the bit array.}  Note: As Squid retrieves objects and stores them in its cache on disk, it adds them to the in-RAM index using a lookup key which is an MD5 hash - the very one discussed above. This means that the values for the Cache Digest hash functions are already available and consequently the operations are extremely efficient!''  (``Key'' here just means hash input, as in ``key-value pair''.)}

>>>>

\tsnote{UPDATE (5/20/16): I'm now convinced that what they call memory size~$m$, when applied to real Bloom filters, is \emph{only} the size of the bit array, and does \emph{not} include a description of the hash functions.  The memory size comparisons that are made throughout the paper are to classical memory lowerbounds that account only for the bitsize of the array. Concretely: in the abstract they say ``... we show there exists a Bloom filter for sets of size~$n$ and error~$\epsilon$, that is secure against~$t$ queries and uses only $O(n\log\frac{1}{\varepsilon} + t)$ bits of memory.  In comparison, $n \log\frac{1}{\varepsilon}$ is the best possible under a non-adaptive adversary.''  The latter bound is the classical one.   If you look in the paper for this actual result, it's in Theorem 6.2.   So, we look at the theorem and the construction that proves it.  It uses a specially constructed function~$g$ and a Cuckoo hashing dictionary~$D$, consisting of two tables~$T_1,T_2$ and two hash functions~$h_1,h_2$.  Here is a quote from the proof ``The final memory of the Bloom filter is the memory of~$D$ and the representation of~$g$.  The dictionary~$D$ consists of $O(n)$ cells, each of size $|g(x)|=O(\log\frac{1}{\varepsilon})$ bits and therefore~$D$ and~$g$ together can be represented using $O(n\log\frac{1}{\varepsilon} + t)$ bits'', where earlier they say ``the representation of~$g$ requires $O(t)$ bits''. (Note that this~$g$ is only used to determined \emph{what} is stored at the indicated array/table positions, not \emph{where}.)  Thus they are not considering the size of the hash functions~$h_1,h_2$ that are used to indicated which cells of~$D$ need to be altered.   So, as I said, I'm now convinced that their Bloom filter syntax does not actually capture real Bloom filters.}

Finally, the security definitions do not give the adversary access to the hash functions that created the representation; effectively, they are secret. \tsnote{Unless they are assuming that the hash functions are fixed, part of the algorithms $B_1$ and $B_2$?  In which case, $A$~knows them too; and the security notion gives~$S$ to~$A$, so...}  This strikes me as quite odd, and seems to miss the point that finding a false positive should be hard, in practice, even if you know that the hash functions are, say,  $h_i(X)=\mathrm{SHA256}(\langle i \rangle \concat X)$.  (If the hash functions are not kept secret, the whole [NY] security notion kind of unravels; the adversary already is given~$S$, so if it knows the hash functions then you might as well just give it the whole Bloom filter data structure.) \tsnote{In the Squid proxy, the hash functions are not secret: you can download the source code, and the docs~\footnote{http://wiki.squid-cache.org/SquidFaq/CacheDigests} (available online even!) tell you that ``The protocol design allows for a variable number of hash functions (k). However, Squid employs a very efficient method using a fixed number - four. {\bf Rather than computing a number of independent hash functions over a URL Squid uses a 128-bit MD5 hash of the key (actually a combination of the URL and the HTTP retrieval method) and then splits this into four equal chunks. Each chunk, modulo the digest size (m), is used as the value for one of the hash functions - i.e. an index into the bit array.}  Note: As Squid retrieves objects and stores them in its cache on disk, it adds them to the in-RAM index using a lookup key which is an MD5 hash - the very one discussed above. This means that the values for the Cache Digest hash functions are already available and consequently the operations are extremely efficient!''  (``Key'' here just means hash input, as in ``key-value pair''.)}
